---
title: "Linear Regression Mini Project"
author: "Anthony Stachowitz"
date: "May 30, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Linear Regression Mini Project
# Exercise 1: least squares regression

   Use the /states.rds/ data set. Fit a model predicting energy consumed
   per capita (energy) from the percentage of residents living in
   metropolitan areas (metro). Be sure to
   
   1. Examine/plot the data before fitting the model
   2. Print and interpret the model `summary'
   3. `plot' the model to look for deviations from modeling assumptions
   
   Select one or more additional predictors to add to your model and
   repeat steps 1-3. Is this model significantly better than the model
   with /metro/ as the only predictor?

### Examine/plot the data before fitting the model

```{r}
states.data <- readRDS("dataSets/states.rds")
states.info <- data.frame(attributes(states.data)[c("names", "var.labels")])
tail(states.info, 8)
sts.eng.mtr <- subset(states.data, select = c("energy", "metro"))
summary(sts.eng.mtr)
plot(sts.eng.mtr)
```

### Print and interpret the model `summary'

```{r}
sat.eng.mod <- lm(energy ~ metro,
              data=states.data)
summary(sat.eng.mod) 
```
**The R-squared is low at 0.1154. this does not look to be a very good regregression model with this data alone. There also seems to be some data points that skew the data a bit**

### `plot' the model to look for deviations from modeling assumptions

```{r}
hist(residuals(sat.eng.mod))
plot(sat.eng.mod)
```





## With additional predictors

### Examine/plot the data before fitting the model

```{r}
sts.eng.hse <- subset(states.data, select = c("energy", "house"))
sts.eng.snt <- subset(states.data, select = c("energy", "senate"))
sts.eng.total <- subset(states.data, select = c("energy", "metro", "house", "senate"))
summary(sts.eng.total)
plot(sts.eng.mtr)
plot(sts.eng.hse)
plot(sts.eng.snt)
```

### Print and interpret the model `summary'

```{r}
sat.eng.mod2 <- lm(energy ~ metro + house + senate,
              data=states.data)
summary(sat.eng.mod2) 
```
**The R-squared is 0.4356. this is a little bit better but we should probably continue to work on it. There still seems to be some data points that skew the data**

### `plot' the model to look for deviations from modeling assumptions

```{r}
hist(residuals(sat.eng.mod2))
plot(sat.eng.mod2)
```

# Exercise 2: Interactions and factors

   Use the states data set.

   1. Add on to the regression equation that you created in exercise 1 by
      generating an interaction term and testing the interaction.

   2. Try adding region to the model. Are there significant differences
      across the four regions?
      
### Add on to the regression equation that you created in exercise 1 by generating an interaction term and testing the interaction.

```{r}
sat.eng.mod2a <- lm(energy ~ metro + house*senate,
              data=states.data)
summary(sat.eng.mod2a)
```
**The regression equation did improve to 0.5567 by making the house and energy dependant on the senate**

### Add region to the model. Are there differences across the four regions?

```{r}
str(states.data$region)
states.data$region <- factor(states.data$region)
sat.eng.mod2b <- lm(energy ~ metro + region + house*senate,
              data=states.data)
summary(sat.eng.mod2b)
```
**There does not seem to be significant diferences with region added**